Pop-up cycleways and pedestrian spaces: a peak into post Covid-19 transport futures

### 2020-05-09 article.Rmd
Update article

1. 'filtered permeability' interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example [@salfordcitycouncil_salford_2020]
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->
2. banning cars and to pedestrianise streets, greatly increasing the width of walkable space, New York's 'Open Streets' initiative being a prominent example [@litman_pandemicresilient_2020], and
3. the reallocation of one or more lanes of traffic to create pop-up cycleways, typically along arterial routes, with lanes reallocated using traffic cones in Auckland providing an early example [@orsman_covid_2020].

>>>>

1. 'filtered permeability', e.g. as shown in [@salfordcitycouncil_salford_2020]

interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example 
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->
2. banning cars and to pedestrianise streets, greatly increasing the width of walkable space, New York's 'Open Streets' initiative being a prominent example [@litman_pandemicresilient_2020], and
3. the reallocation of one or more lanes of traffic to create pop-up cycleways, typically along arterial routes, with lanes reallocated using traffic cones in Auckland providing an early example [@orsman_covid_2020].

### 2020-05-09 conversation.Rmd
Update article

Local and national governments worldwide are still working out how best to respond to these changes to lif. Hundreds of kilometres of temporary infrastructure being put in place in dozens of cities worldwide, from [Park Lane in London](https://www.forbes.com/sites/carltonreid/2020/05/06/pop-up-cycleway-for-park-lane-as-tenfold-increase-in-cycling-predicted-for-london/#48aad0705b1e "") to [Martin Luther King Jr Drive in Philadelphia](https://www.theguardian.com/world/2020/apr/11/world-cities-turn-their-streets-over-to-walkers-and-cyclists ""), [Auckland](https://www.roadtraffic-technology.com/news/nz-govt-extra-wide-footpaths/ "") to [Mexico City](https://bicitekas.org/sites/default/files/public/manuales/propuesta_ciclovias_temporales_cdmxvfinal.pdf ""), never has there been such a need for affordable, healthy and socially isolated transport that does not create the fumes that emerging evidence links to coronavirus susceptibility. With the rush to act, there is a great need for evidence of *where* new interventions should be prioritised. As with the medical science, research is needed now. Methods developed to identify locations of high walking and cycling potential can help ensure that the ‘pop-up’ infrastructure that goes in now is effective, safe, and placed where it is most needed.

>>>>

Local and national governments worldwide are still working out how best to respond to these changes.
Hundreds of kilometres of temporary infrastructure being put in place in dozens of cities worldwide, from [Park Lane in London](https://www.forbes.com/sites/carltonreid/2020/05/06/pop-up-cycleway-for-park-lane-as-tenfold-increase-in-cycling-predicted-for-london/#48aad0705b1e) to [Martin Luther King Jr Drive in Philadelphia](https://www.theguardian.com/world/2020/apr/11/world-cities-turn-their-streets-over-to-walkers-and-cyclists ""), [Auckland](https://www.roadtraffic-technology.com/news/nz-govt-extra-wide-footpaths/) to [Mexico City](https://bicitekas.org/sites/default/files/public/manuales/propuesta_ciclovias_temporales_cdmxvfinal.pdf), never has there been such a need for affordable, healthy and socially isolated transport that does not create the fumes that emerging evidence links to coronavirus susceptibility. With the rush to act, there is a great need for evidence of *where* new interventions should be prioritised. As with the medical science, research is needed now. Methods developed to identify locations of high walking and cycling potential can help ensure that the ‘pop-up’ infrastructure that goes in now is effective, safe, and placed where it is most needed.
